### 2020-04-08 writeup/setup.tex
revise intro

First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer. [\textbf{done}]

	{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs. [\textbf{1/2 done}]
\end{enumerate}

>>>>

First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
	With multi-task training, since the training objective balances the losses from both the source and target tasks, the trained model can have worse performance for the target task.
	In particular, if model shift is too large, we get negative transfer from multi-task training. [\textbf{done}]
	%{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	%The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks. [\textbf{done}]
	\item {\bf Covariate shift affects the rate of transfer:} next we show that fine tuning the multi-task model on the target task can correct the negative transfer.
	We further show that covariate shift controls the rate in which transfer occurs. [\textbf{1/2 done}]
\end{enumerate}
